\documentclass[10pt,a4paper]{amsart}
\usepackage[utf8]{inputenc}
\usepackage[french]{babel}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[left=2.5cm,right=2.5cm,top=3cm,bottom=3cm]{geometry}

\author{Brachet Matthieu}
\title{Numerical resolution of three dimensional PDEs on the Sphere, in climatology and oceanography.}
\date\today

\def\REF{\textbf{REF} }
\begin{document}
\maketitle

In \cite{Croisille-10, Croisille-12, Brachet-Croisille}, a finite difference scheme for partial differential equation is introduced and studied. The grid used is the Cubed-Sphere grid. This grid is quasi cartesian and composed of six patch matching with faces of a cube.
The calculation of the approximated divergence, gradient and curl operator is based on the evaluation of approximated derivatives in a periodic context. Each derivative is made with an hermitian compact scheme. This method is possible thanks to the square like aspect of each panel and thanks to a great circle structure permitting to construct the Cubed-Sphere grid.

The time scheme is an explicit four order Runge-Kutta method in which a space filtering procedure is added on each time step. A Courant-Friedrich-Levy condition (CFL) depending of the space step and characteristic velocity is used.
The full method gives very good results on Shallow Water equation and Linearized Shallow Water equation on a broad series of tests cases in oceanography and climatology.

The main goal of this research project is to extend the method to solve three dimension problems like Global Non-hydrostatic fluid equation. For example, I intend to investigate the Runge-Kutta-Rosenbrock scheme and splitting scheme used to solve the Shallow Water equations as in \cite{Ullrich, Choi-Hong}.

Considering the difference of scale between the tangential dimension and the vertical dimension, an explicit time scheme is too restrictive considering the CFL condition. An important objective is to obtain a fully implicit scheme. Despite each cost, this kind of scheme clearly a sorrow study. 

The quasi-cartesian structure of the Cubed-Sphere permits a good representation of Spherical Harmonics. Then, spherical harmonics interpolation process can be introduced and study. This way concern fast solver and fast evaluation of each operator.

A mathematical analysis of the method will be undertaken. This analysis will concern accuracy of the method but also the conservation properties and stability of the scheme. 

In order to analyze the robustness and the accuracy of the scheme, three dimensional test cases will considered. 

The ultimate goal is the development of an operational code able to unable complete spherical models in the context of hight order accurate finite different schemes.

\bibliographystyle{plain}
\bibliography{bibox_JPC}
\end{document}