%%%%%%% DO NOT MODIFFY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper, 10pt]{amsart}


\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx,color}

\usepackage[latin1]{inputenc}  %%PC ou Unix

\def\myAbstract#1{
{\vspace{0.2cm}\flushleft\sffamily\bfseries\Large Abstract\vspace{0.2cm}} 
\\
#1}

\def\myTalk#1{
\section*{#1}
}

\def\myMini#1{
{\flushleft\sffamily\bfseries\LARGE #1\vspace{1cm}}  
}

\def\myAuthor#1#2#3#4{
{\noindent #1 #2 \index{#2@#2, #1} \\ #3 \\ #4 \\}}

\def\myCoauthor#1#2#3#4{  
{\noindent #1 #2 \index{#2@#2, #1} \\ #3 \\ #4 \\}}

\def\myLoc#1 {{\flushleft{\bf Chairman:   #1 \\}}}

\def\myItem#1#2{\item #1\\ #2}
%%%%%%% DO NOT MODIFFY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\myTalk{Numerical approximation of propagation problems on the sphere using a compact scheme}


\bigskip
\myAuthor{M.}{Brachet}
{Institut Elie Cartan de Lorraine} {matthieu.brachet@univ-lorraine.fr}

\myCoauthor{J.-P.}{Croisille}
{Institut Elie Cartan de Lorraine} {jean-pierre.croisille@univ-lorraine.fr}


 \myAbstract{This poster presents numerical results for the shallow water equations on  a rotating shere  using the compact scheme introduced in \cite{C2015}. The scheme uses the Cubed-Sphere grid and is based on a centered finite difference scheme. The discretization is performed by a Runge-Kutta method combined with a high-frequencies filtering procedure. Numerical results are displayed  for several classical test cases  \cite{BCyear, G2004}. Numerical results, for an associated  quadrature method on the Cubed Sphere, permitting to assess the conservation properties of the scheme will also be displayed.}
 
 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bigskip
 \noindent
 {\bfseries Keywords}. {\small Cubed-Sphere grid, Compact scheme, Hermitian scheme, quadrature formula.  }
 
 

   
 %%\vskip10pt
%{\bf References}
\bibliographystyle{abbrv}
%\bibliography{afeti}
\begin{thebibliography}{10}
\bibitem{BCyear} {\sc M. Brachet, J.-P. Croisille}, \textit{Numerical simulations of propagation problemes on the sphere
using a compact scheme}, preprint.

\bibitem{C2015} {\sc J.-P. Croisille}, \textit{Hermitian approximation of the spherical divergence on the Cubed-Sphere}, J.
Comp. App. Maths., 280, 2015, pp. 188-201.

\bibitem{G2004} {\sc J. Galewsky, R. Scott, K. Richard and L. M. Polvani}, \textit{An initial-value problem for testing
numerical models of the global shallow-water equations}, Tellus A , 56, 2004, pp. 429?440.

\end{thebibliography}
%\include{mytalk}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}      
