%%%%%%% DO NOT MODIFFY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper, 10pt]{amsart}


\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx,color}
\usepackage{cite}
\usepackage{filecontents}


\usepackage[latin1]{inputenc}  %%PC ou Unix
\usepackage[english,francais]{babel}

\newcommand{\Lp}{L^p}
\newcommand{\N}{\mathbb{{N}}}
\newcommand{\R}{\mathbb{{R}}}
\newcommand{\Wp}{W^{1,p}}
\newcommand{\Wkp}{W^{k,p}}
\newcommand{\Ho}{H_{0}^{1}(\Omega)}
\newcommand{\dOmega}{{\partial\Omega}}

\def\myAbstract#1{
{\vspace{0.2cm}\flushleft\sffamily\bfseries\Large  Abstract {\normalfont \sl  }\vspace{0.2cm}} 
\\
#1}

\def\myTalk#1{
\section*{#1}
}

\def\myMini#1{
{\flushleft\sffamily\bfseries\LARGE #1\vspace{1cm}}  
}

\def\myAuthor#1#2#3#4{
{\noindent #1 #2 \index{#2@#2, #1} \\ #3 \\ #4 \\}}

\def\myCoauthor#1#2#3#4{  
{\noindent #1 #2 \index{#2@#2, #1} \\ #3 \\ #4 \\}}

\def\myLoc#1 {{\flushleft{\bf Chairman:   #1 \\}}}

\def\myItem#1#2{\item #1\\ #2}


 %%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
\let\bb\mathbb
\def \R {{\relax{\bb R}}}
 \def  \N {\relax{\bb N}}
\def \Z {\relax{\bb Z}}
\def \C {\relax{\bb C}}


%%%%%%% DO NOT MODIFFY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\myTalk{\selectlanguage{english}{ Numerical approximation of propagation problems on the sphere using a compact scheme }}

 
\bigskip
\myAuthor{Matthieu}{Brachet}
{Université de Lorraine\\ Institut Elie Cartan de Lorraine}
 {matthieu.brachet@univ-lorraine.fr}

\myCoauthor{Jean-Pierre}{Croisille}
{Université de Lorraine\\ Institut Elie Cartan de Lorraine} {jean-pierre.croisille@univ-lorraine.fr }
 

\myAbstract{\selectlanguage{english}
{This poster presents numerical results for the shallow water equations on  a rotating shere  using the compact scheme introduced in \cite{C2015}. The scheme uses the Cubed-Sphere grid and is based on a centered finite difference scheme. The discretization is performed by a Runge-Kutta method combined with a high-frequencies filtering procedure. Numerical results are displayed  for several classical test cases  \cite{BCyear, G2004}. Numerical results, for an associated  quadrature method on the Cubed Sphere, permitting to assess the conservation properties of the scheme will also be displayed.
}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\\
\\ {\bfseries Keywords}. {\small Cubed-Sphere grid, Compact scheme, Hermitian scheme, quadrature formula.}
\\[5mm]


\noindent
\selectlanguage{french}
\textbf{\textsf{\large R\'esum\'e.}} {\bfseries 
Approximation numérique de problèmes de propagation sur la sphère avec un schéma compact}.
{Ce poster présente les résultats numériques de l'équation Shallow Water sur une sphère en rotation utilisant le schéma compact introduit dans \cite{C2015}. Le schéma utilise la grille Cubed-Sphere et est basée sur un schéma aux différences finies centré. La discrétisation est effectuée avec une méthode de Runge-Kutta combinée à une procédure de filtrage des hautes fréquences. Les résultats numériques sont présentés sur de nombreux tests classiques \cite{BCyear, G2004}.
Les résultats numériques pour une méthode de quadrature associée sur la Cubed-Sphere permettant d'accéder aux propriétés de conservation du schéma seront aussi affichés.
}



 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bigskip
 \noindent
 {\bfseries Mots cl\'es}. {\small Grille Cubed-Sphere, Schéma compact, Schéma hermitien, formule de quadrature.}
 
  

\bigskip
\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{abbrv}
 \begin{thebibliography}{10}
\bibitem{BCyear} {\sc M. Brachet, J.-P. Croisille}, \textit{Numerical simulations of propagation problemes on the sphere
using a compact scheme}, preprint.

\bibitem{C2015} {\sc J.-P. Croisille}, \textit{Hermitian approximation of the spherical divergence on the Cubed-Sphere}, J.
Comp. App. Maths., 280, 2015, pp. 188-201.

\bibitem{G2004} {\sc J. Galewsky, R. Scott, K. Richard and L. M. Polvani}, \textit{An initial-value problem for testing
numerical models of the global shallow-water equations}, Tellus A , 56, 2004, pp. 429?440.


\end{thebibliography}

 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}      

