\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Brachet M., Croisille J.-P., \\
\small{\sl Math. Dept., IECL, UMR CNRS 7502, Univ. Lorraine, FRANCE}}
\title{Abstract - SIAM 2016}

\begin{document}
\maketitle

In this presentation, we give an account on recent results obtained
with a finite difference scheme on the Cubed-Sphere grid, \cite{Ronchi-Iacono-Paolucci, Croisille2013}. The scheme 
is compact in the sense of \cite{Lele1991}. 
Numerical results on benchmark advection test 
cases in Numerical Climatology  \cite{Nair2008} exhibiting fourth-order accuracy  will be shown \cite{Brachet2016}.
 Test-cases involving the 
linearized SW equations will be displayed as well. Furthermore first results
on the mathematical analysis of the scheme will be given.

\begin{thebibliography}{9}

\bibitem{Brachet2016}
         M. Brachet, J.-P. Croisille
         \emph{:  Numerical simulation of vortex propagation problems on the Cubed-Sphere using a compact scheme.}
         Preprint,
         2016.

\bibitem{Croisille2013}
         J.-P. Croisille,
         \emph{: Hermitian compact interpolation on the Cubed-Sphere grid, Jour. Sci. Comp.}
          57,1,
          2013, 
		pp.193-212.

\bibitem {Ronchi-Iacono-Paolucci} C. Ronchi, R. Iacono and P. S. Paolucci,
\emph{The Cubed Sphere: A New Method for the Solution of Partial
Differential Equations in Spherical Geometry, J. Comput. Phys.} 124,1996, pp. 93--114.

\bibitem{Lele1991}
         Sanjiva K. Lele
         \emph{:  Compact Finite Difference Schemes with Spectral-like Resolution}.
         Center for turbulence Research, NASA-Ames Research Center
         Journal of computational physics,
         1991.
         
\bibitem{Nair2008}
         Ramachandran D. Nair and Christiane Jablonowski,
        \emph{:  Moving vortices on the sphere: a test case for horizontal advection problems.}
        Mon. Wea. Rev.,
        136,
        699–711.

		
\end{thebibliography}

\end{document}